Comparing binsegRcpp with other implementations of binary segmentation for changepoint detection

### 2022-08-08 article.Rnw
orcid
ref line fig

%% - \author{} with primary affiliation (and optionally ORCID link)
%% - \Plainauthor{} without affiliations
%% - Separate authors by \And or \AND (in \author) or by comma (in \Plainauthor).
%% - \AND starts a new line, \And does not.
\author{Toby Dylan Hocking~\orcidlink{0000-0002-3146-0865}\\Northern Arizona University}
\Plainauthor{Toby Dylan Hocking}

@@

%% - \Abstract{} almost as usual
\Abstract{ Binary segmentation is a classic algorithm for detecting
 changepoints in sequential data. In theory it should be extremely fast for $N$ data and $K$ segments, $O(N K)$ in the worst case, and $O(N \log K)$ in the best case. In practice existing implementations such as ruptures (\proglang{Python} module) and changepoint (\proglang{R} package) are much slower, and in fact sometimes do not return a correct result. We present the \proglang{R} package \pkg{binsegRcpp}, which provides an efficient C++ implementation of binary segmentation, and always returns correct results. We discuss some advanced C++ coding techniques which were used to avoid repetition, for efficiency, and for readability.  We additionally include detailed theoretical and empirical comparisons with other implementations of binary segmentation in \proglang{R} packages \pkg{fpop}, \pkg{blockcpd} and \pkg{wbs}. }

>>>>

%% - \author{} with primary affiliation (and optionally ORCID link)
%% - \Plainauthor{} without affiliations
%% - Separate authors by \And or \AND (in \author) or by comma (in \Plainauthor).
%% - \AND starts a new line, \And does not.
\author{Toby Dylan Hocking~\orcid{0000-0002-3146-0865}\\Northern Arizona University}
\Plainauthor{Toby Dylan Hocking}

@@

%% - \Abstract{} almost as usual
\Abstract{ Binary segmentation is a classic algorithm for detecting
  changepoints in sequential data. In theory, using a simple loss
  function like Gaussian or Poisson, binary segmentation should be
  extremely fast for $N$ data and $K$ segments, $O(N K)$ in the worst
  case, and $O(N \log K)$ in the best case. In practice existing
  implementations such as ruptures (\proglang{Python} module) and
  changepoint (\proglang{R} package) are much slower, and in fact
  sometimes do not return a correct result. We present the
  \proglang{R} package \pkg{binsegRcpp}, which provides an efficient
  C++ implementation of binary segmentation, and always returns
  correct results. We discuss some advanced C++ coding techniques
  which were used to avoid repetition, for efficiency, and for
  readability.  We additionally include detailed theoretical and
  empirical comparisons with other implementations of binary
  segmentation in \proglang{R} packages \pkg{fpop}, \pkg{blockcpd} and
  \pkg{wbs}. }
